Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
cite 0brist 2010, Bardeli 2010

As stated in the introduction, the field of ecoacoustics is relatively young, but significant works are worth mentioning.
One avenue of research, originated in bioacoustics, intends to retrieve the species that produced a given sonic event of relatively short duration, in order to link animal vocalization with behavior\cite{au2008principles, stowell2014large}.
A more recent paradigm processes the audio stream at hand in a holistic way, as it describes the auditory environment over larger temporal scales, without assuming that one single species is present throughout the recording. Automated systems belonging to this paradigm aim at inferring global properties of bioacoustic scenes, including biodiversity indices \vl{ref}, migration patterns \vl{ref}, as well as regions of particular interest before human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.

>>>>

As stated in the introduction, the field of ecoacoustics is relatively young, but significant works are worth mentioning.
One avenue of research, originated in bioacoustics, intends to retrieve the species that produced a given sonic event of relatively short duration, in order to link animal vocalization with behavior\cite{au2008principles, stowell2014large}.
A more recent paradigm processes the audio stream at hand in a holistic way, as it describes the auditory environment over larger temporal scales, without assuming that one single species is present throughout the recording. Automated systems belonging to this paradigm aim at inferring global properties of bioacoustic scenes, including biodiversity indices \cite{Obrist2010}, trends in population sizes \cite{Bardeli2010}, as well as regions of particular interest before human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.
